Regression

### 2018-01-30 paper/R/02_cleanAndCombine.Rmd
add ownership covariates

## Preparation
### Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data

### without stemming
# processed1 <- textProcessor(btw$text_cleaned, metadata = btw[,c("site","text_cleaned","month")],
#                            wordLengths = c(2,Inf),
#                            lowercase = F,
#                            removestopwords = F,
#                            removenumbers = F,
#                            removepunctuation = F,
#                            stem = F)
# out1 <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
###

processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
out$meta$site <- as.factor(out$meta$site)

save(btw, out, file="../output/btw_combined.Rda")
```

>>>>

## Preparation
```{r}
btw <- btw %>% 
  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private"))
```

### Build Corpus
```{r eval=FALSE, include=FALSE}
# Process data

### without stemming
processed1 <- textProcessor(btw$text_cleaned1, metadata = btw[,c("ownership","text_cleaned1","month")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out_ownership <- prepDocuments(processed1$documents, processed1$vocab, processed1$meta)
out_ownership$meta$ownership <- as.factor(out_ownership$meta$ownership)
###

# processed <- textProcessor(btw$text_cleaned1, metadata = btw[,c("site","text_cleaned1","month")],
#                            wordLengths = c(2,Inf),
#                            lowercase = F,
#                            removestopwords = F,
#                            removenumbers = F,
#                            removepunctuation = F,
#                            stem = F)
# out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
# out$meta$site <- as.factor(out$meta$site)

save(btw, out_ownership, file="../output/btw_comb_ownership.Rda")
```

### 2018-01-30 paper/R/paper.Rmd
add ownership covariates

library(igraph)
library(corrplot)
library(ggpmisc)
library(ggiraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(viridis)     # Viridis color scales

@@

```{r}
# Topic 3
plotNewspaperHistogram(1)
```

@@

```{r}
summary(effect)
```

@@

### Distance metric

>>>>

library(igraph)
library(corrplot)
library(patchwork)
library(ggpmisc)
library(ggiraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(viridis)     # Viridis color scales

@@

```{r}
# Topic 1
plotNewspaperHistogram(1)
```

### by ownership
plots the expected proportion of topic use in public media minus the expected proportion of topic use in private media. Thus topics more associated with public media appear to the right of zero.

```{r}
freq <- tapply(stmOut$theta[,1], stmOut$settings$covariates$betaindex, mean)
freq <- as.data.frame(freq) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels,
           topic = 1)

for(i in 2:40) {
  freq1 <- tapply(stmOut$theta[,i], stmOut$settings$covariates$betaindex, mean)
  freq1 <- as.data.frame(freq1) %>% 
    transmute(site=stmOut$settings$covariates$yvarlevels,
           topic = i,
           freq = freq1)

  freq <- rbind(freq, freq1)
}

freq <- freq %>%
  mutate(ownership = ifelse(site == "Tagesschau.de", "public", "private")) %>%
  group_by(topic, ownership) %>%
  summarise(freq_mean = mean(freq)) %>%
  spread(ownership, freq_mean) %>%
  mutate(freq_diff = public - private) %>%
  mutate(value = ifelse(freq_diff>=0, 1,0)) %>%
  left_join(., topics.df, by = "topic")
```

```{r}
p1 <- ggplot(freq, aes(reorder(topic_name, freq_diff), freq_diff,
                 fill = factor(value))) +
  geom_col(show.legend = F) +
  scale_fill_manual(values = col[c(1,3)]) +
  coord_flip() +
  theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10)) +
    labs(x="", y="difference in expected frequency (public-private)")

ggsave(plot = p1, filename = "../figs/topic_proportion_diff.png", device = "png",width = 8, height = 12,
dpi = 600)
```

@@

```{r}
save.image("stm_newsdata.RData")
```

@@

### Distance metric
Compute different metrices and compare them.
